Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-22 latex/article.tex
wip

\paragraph{Hierarchical Decomposition.}  As discussed above, best
results in terms of texture fetch can be obtained by the approach
presented in Fig.~\ref{fig:approx2}-$b$. At each vertex, the
computation algorithm would consist in a recursive decomposition of
the domain such that a cell is subdivided if it does not belong to
$B_R(\vx)\cap\Shape$. However, on GPU hardware, this approach is
highly inefficient since the hardware optimizes the parallelism only
when the micro-program described in the shader has a predictive
execution flow. Hence, implementing the recursive algorithm (or its
de-recursified version) requires a lot of branches (conditional
\emph{if} tests) in the flow. Instead of implementing this approach,
we have considered a fast hierarchical approximation following
Fig.~\ref{fig:approx2}-$a$: for a given radius $R$, we precompute a
hierachical decomposition of $B_R$. Such decomposition is made of
octree cells at different resolutions. At a given MC vertex $\vx$, the
algorithm becomes simple since we just scan  the ball cells and estimate
the area (or other moments) from the mipmap values associated to this
cell. Note that cells in the $B_R$ decomposition may not be aligned
wuth mipmap cells. However, we can use GPU mipmap functionalities
which interpolates mipmap values if we probe at non-discrete
positions. For a given radius $R$, the expected number of cells on
$B_r$ is in $O(\log{R})$.

@@

@@

>>>>

\paragraph{Hierarchical Decomposition.}  As discussed above, best
results in terms of texture fetch can be obtained by the approach
presented in Fig.~\ref{fig:approx2}-$b$. At each vertex, the
computation algorithm would consist in a recursive decomposition of
the domain such that a cell is subdivided if it does not belong to
$B_R(\vx)\cap\Shape$. However, on GPU hardware, this approach is
highly inefficient since the hardware optimizes the parallelism only
when the micro-program described in the shader has a predictive
execution flow. Hence, implementing the recursive algorithm (or its
de-recursified version) requires a lot of branches (conditional
\emph{if} tests) in the flow. Instead of implementing this approach,
we have considered a fast hierarchical approximation following
Fig.~\ref{fig:approx2}-$a$: for a given radius $R$, we precompute a
hierachical decomposition of $B_R$. Such decomposition is made of
octree cells at different resolutions. At a given MC vertex $\vx$, the
algorithm becomes simple since we just scan the ball cells and
estimate the area (or other moments) from the mipmap values associated
to this cell. Note that cells in the $B_R$ decomposition may not be
aligned wuth mipmap cells. However, we can use GPU mipmap
functionalities which interpolates mipmap values if we probe at
non-discrete positions. For a given radius $R$, the expected number of
cells on $B_r$ is in $O(\log{R})$. Implementation details on the
hierarchical octree representation can be found in the supplementary
material (see Section \ref{sec:discussion}).

@@

\begin{figure}
  \begin{center}
    \subfigure[]{\framebox{octa $l_4$}}
   \subfigure[]{\framebox{octa $l_3$}}
   \subfigure[]{\framebox{octa $l_2$}}
   \subfigure[]{\framebox{octa $l_1$}}
   \subfigure[]{\framebox{octa $l_0$}}
  \end{center}
  \caption{fig multiresolution, courbure moyenne par ex}
  \label{fig:refine}
\end{figure}
\todo[inline]{blabla experiments}

@@

\begin{figure}
  \begin{center}
    \subfigure[]{\framebox{K}}
   \subfigure[]{\framebox{H}}
   \subfigure[]{\framebox{DIR1}}
   \subfigure[]{\framebox{DIR2}}
   \subfigure[]{\framebox{normales}}\\
    \subfigure[]{\framebox{K}}
   \subfigure[]{\framebox{H}}
   \subfigure[]{\framebox{DIR1}}
   \subfigure[]{\framebox{DIR2}}
   \subfigure[]{\framebox{normales}}

  \end{center}
  \caption{fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.}
  \label{fig:full}
\end{figure}

\todo[inline]{blabla experiments}

For dynamic datasets, we consider a time varying impicit
surface. Since it would have been to expensive to update the a mipmap texture
of densities at each time step, we simply evaluate the implicit
expression at each vertex of a cell to decide if such cell is included
or not into $B_R(\vx)\cap X$.
\todo[inline]{blabla experiments}
